First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
implement stepans 3rd comments

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of Deeply Virtual Compton 
Scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer. A new 
Radial Time Projection Chamber was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries are significantly larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, the chiral even Generalized 
Parton Distribution $H_{A}$ of $^4$He. This pioneering measurement leads 
the way toward the 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

Rich information on Quantum Chromodynamics (QCD) lies in the internal structure 
of hadrons. In the recent past, development of the Generalized Parton 
Distributions (GPDs) framework has offered a possibility to obtain new 
information about the momentum and spatial degrees of freedom of the quark and 
gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.

The most promising way to access GPDs experimentally is through the measurement 
of Deep Virtual Compton Scattering (DVCS), i.e.  the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN.  The vast majority of these measurements focused on the study of proton 
structure and allowed extraction of the tomography of the nucleon (for details 
on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

@@

The coherent nuclear DVCS reaction, $eA \rightarrow e' A' \gamma$, is difficult 
to measure due to its small cross section and the necessity to ensure 
exclusivity of the reaction, i.e. the target nucleus. Figure \ref{fig:diags} 
illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
small squared momentum transfer $t=(p-p')^{2}$ (in terms of the electron, 
$k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag diagram can be 
factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part 
includes the photon-quark interaction and is calculable in perturbative QCD.  
The non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron. The GPDs depend on the three variables $x$, 
$\xi$ and $t$ as introduced in Figure \ref{fig:diags}. The parameter $\xi$
relates to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and  
$\nu=k^0-k^{0\prime}$, the $t$ is squared momentum transfer to the target. The 
parameter $x$ is the quark's internal loop momentum fraction and cannot be 
accessed experimentally. In the experiment we measure Compton Form
Factors (CFF) \cite{Guidal:2013rya}, complex amplitudes defined as:

@@

The main challenge in studying nuclear DVCS is ensuring the exclusivity of the 
reaction. Until now, the only available data on nuclear DVCS was from the 
HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity was based only on 
kinematic cuts on the measured scattered electron and real photon. That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee the nucleus 
remains intact and that the reaction did not occur on a bound nucleon. The 
CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
optimized for DVCS measurements 
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, so we 
built a specialized radial time projection chamber (RTPC) for detection of a 
low energy recoiling light nuclei in order to ensure exclusivity of the 
reaction. The $^4$He nucleus is an ideal experimental target in this regard, as 
it is light enough to be detected in such a setting, while it
is subject to significant nuclear effects \cite{JSeely} and has rather high 
density.  A helium target leads to another important advantage, as the number of GPDs 
defined for a hadron depends on its spin. The structure of a spin zero nucleus, such as 
$^4$He, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case. This significantly
simplifies the interpretation of the data and allows a model independent
extraction of the $^4$He CFF ($\mathcal{H}_{A}$) presented at the
end of this letter.

@@

The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed in the center of CLAS. For DVCS 
experiments, the CLAS baseline design \cite{Mecking:2003zu} is supplemented 
with an inner calorimeter (IC) and a solenoid. The IC extends the photon 
detection acceptance of CLAS to polar angles as low as 4$^{\circ}$. The 
low-energy M\o{}ller electrons produced in the target form a very high rate 
background that is suppressed by a 5 Tesla solenoid placed around the target.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. In Figure~\ref{fig:RTPC} a picture of 
RTPC installed in the experimental hall, and the rendering showing detector 
components and the $^4$He detection concept are presented. The $^4$He gaseous 
target, a $25$ cm long, $27~\mu$m wall Kapton straw, in the center was part of 
the RTPC assembly. The detector was calibrated specifically for the detection 
of $^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one 
electron, one $^4$He, and at least one photon are detected in the final state.
Electrons are identified using measured momentum, time and energy in fiducial 
volume of CLAS drift chambers, Cerenkov counters, scintillator counters, and 
electromagnetic calorimeters. The $^4$He are identified in the RTPC using time, 
track quality, and energy loss cut for tracks in the fiducial region. In 
addition, we apply a vertex matching cut to ensure that the electron and helium
nucleus originate from the same position. The photons are detected in either
the IC or the CLAS electromagnetic calorimeter. Note that even though the DVCS 
reaction has only one real photon in the final state, events with more than one 
good photon are not discarded at this stage. This is motivated by the fact 
that, while soft photons are likely to be produced in random coincidence, they 
cannot be mistaken for the large energy DVCS photons ($>2$ GeV).
The most energetic photon is always considered as the DVCS photon candidate.

@@

%asymmetries
In this work, the physics observable extracted using coherent DVCS events is
the Beam Spin Asymmetry (BSA). The BSA on unpolarized target (U), $A_{LU}$, is 
measurable by the difference of cross sections of the reaction at opposite beam 
helicities normalized to the total cross section. It is written as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
section for a positive (negative) beam helicity. Experimentally, $A_{LU}$ 
can be expressed in terms of the measured number of events in each 
beam-helicity state ($N^{+}$, $N^{-}$) as:
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
of DVCS events detected with positive and negative electron helicity with 
respect to the beam direction. In this ratio most of uncertainties of the 
experimental normalization and in detector efficiencies will cancel out.

The DVCS reaction is experimentally indistinguishable from the well-known 
Bethe-Heitler (BH) process, where the final photon is emitted either from the 
incoming or the outgoing leptons. At leading twist and leading order, the 
deeply virtual photon production cross section is composed of BH, DVCS, and 
interference terms. While the BH is not sensitive to GPDs and does not carry 
information about the partonic structure of the hadronic target, its 
interference with the DVCS reaction is sensitive to GPDs enhancing the DVCS 
small cross section at the kinematical regions explored at Jefferson Lab. The 
amplitudes of the three terms can be approximated as a finite sum of Fourier 
harmonics, as shown for the nucleon in \cite{Belitsky:2001ns} and for the 
spin-zero targets in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these 
approximations, the beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can 
then be expressed as:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_i$’s are kinematic 
factors that depend on azimuthal angle $\phi$, the nuclear form factor 
$F_A(t)$, $Q^2$, and $x_B$. These factors are expressed as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi),\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} 
   \cos(2\phi),\\ \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
C_{++}(0) +  C_{++}(1) cos(\phi) \right),\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2},
\end{eqnarray}
\normalsize
where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
in the leptonic tensor.  The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz}.  We see that by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

In this work the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
for a wide range of kinematics. We identified two main backgrounds to our 
measurement, accidental coincidences and exclusive coherent $\pi^0$ production.  
The accidentals have particles originating from different events, and we 
estimate their  contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with an electron and 
helium originating from different vertices. Regarding the $\pi^0$ production, 
it can easily be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the importance of this background, we developed an event generator 
calibrated on the experimental yield of exclusive $\pi^0$ measured by our 
experiment. We used this generator together with a GEANT3 simulation of our 
detector to estimate the ratio between the number of $\pi^0$ events where the 
two photons are detected and those that is misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data.  Depending on the kinematics, we found contaminations of 
2 to 4\%. The study of systematics uncertainties showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%). However, added quadratically,the total systematic 
uncertainty is about 10\%, which is significantly smaller than statistical 
uncertainties in all kinematical bins.

Due to limited statistics, dependence on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In Figure \ref{fig:alu}, $A_{LU}$ 
for the three sets of binning is presented. The curves on the plots are fits 
with the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and 
imaginary part of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit. 
In Figure \ref{fig:alu90} the $Q^2$, $x_{B}$, and $-t$-dependencies of the 
fitted $A_{LU}$ signals at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and 
$-t$-dependencies are compared to theoretical calculations performed by 
S.~Liuti and K.~Taneja \cite{simonetta_2}. The model relies on the impulse 
approximation and uses advanced spectral functions of nuclei. The calculations 
are at slightly different kinematics than our data but still provide some 
guidance. The experimental results appear to have larger asymmetries than the 
calculations. These differences may arise from nuclear effects, such as 
long-rage interactions, which are not taken into account in the model.

@@

The $Q^2$, $X_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
Figure \ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
and non-interacting nucleons, where these nucleons interact independently with 
the probe. The Convolution-Dual model is based on nucleon GPDs from the dual 
parametrization \cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon 
GPDs  from the VGG model and is based on the double distributions ansatz 
\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on 
the impulse approximation and uses advanced spectral functions of  nuclei that 
account for all configurations of the final nuclear system and the binding 
effects between the nucleons.

The results in Figure \ref{fig:CFF_HA} show that the extraction of the CFF
from the beam spin asymmetry is possible without any model dependent 
assumptions. The amplitude and the dependencies observed as a function of 
$Q^{2}$, $x_B$, and $-t$ are in agreement 
with the theoretical calculations. One can see a difference between the 
precision of the extracted imaginary and real parts, which is expected from
Eq.~\ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. While the 
accuracy of our results does not allow to discriminate between the models, they 
demonstrate possibility of extraction of the CFF of spin 0 target in a model 
independent way.

>>>>

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of coherent Deeply Virtual Compton 
Scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF machine at Jefferson Lab incident on a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer. A new 
Radial Time Projection Chamber was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries are larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, the real and imaginary of the $^4$He Compton Form Factors, $\cal H_A$, which are functions of the Generalized Parton Distribution $H_A$. 
This pioneering measurement of coherent Deeply Virtual Compton Scattering on the $^4$He nucleus, with a fully exclusive final state via nuclear recoil tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

Rich information on Quantum Chromodynamics (QCD) can be extracted from the internal structure 
of hadrons. In the recent past, development of the Generalized Parton 
Distributions (GPDs) framework has offered a possibility to obtain new 
information about the momentum and spatial degrees of freedom of the quarks and 
gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.

The most promising way to access GPDs experimentally is through the measurement 
of Deep Virtual Compton Scattering (DVCS), i.e.  the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of worldwide efforts 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN.  The vast majority of these measurements focused on the study of proton 
structure and allowed extraction of the tomography of the nucleon (for details 
on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

@@

One must overcome two major experimental challenges in measuring coherent nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section of coherent scattering is suppressed due to the nuclear form factor, and second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
%The coherent nuclear DVCS reaction, $eA \rightarrow e' A' \gamma$, is difficult 
%to measure due to its small cross section and the necessity to ensure 
%exclusivity of the reaction, i.e. the target nucleus.
Figure \ref{fig:diags} 
illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
small squared momentum transfer $t=(p-p')^{2}$ (in terms of the electron, 
$k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag diagram can be 
factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part 
includes the photon-quark interaction and is calculable in perturbative QCD.  
The non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron. The GPDs depend on the three variables $x$, 
$\xi$ and $t$ as introduced in Figure \ref{fig:diags}. The parameter $\xi$
relates to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and  
$\nu=k^0-k^{0\prime}$, the $t$ is squared momentum transfer to the target. The 
parameter $x$ is the quark's internal loop momentum fraction and cannot be 
accessed experimentally. In the experiment we measure Compton Form
Factors (CFF) \cite{Guidal:2013rya}, complex amplitudes defined as:

@@

%The main challenge in studying nuclear DVCS is ensuring the exclusivity of the reaction. 
Until now, the only available data on nuclear DVCS was from the 
HERMES experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based only on 
kinematic cuts on the measured scattered electron and real photon. That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee the nucleus 
remains intact and that the reaction did not occur on a bound nucleon. The 
CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
optimized for DVCS measurements 
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.

In order to measure DVCS on $^4$He with a fully exclusive final state, we 
built a specialized radial time projection chamber (RTPC) for detection and identification of
low energy recoiling light nuclei in order to ensure exclusivity of the 
reaction. The $^4$He nucleus is an ideal experimental target in this regard, as 
it is light enough to be detected in such a setting, while it
is subject to significant nuclear effects \cite{JSeely} and has rather high 
density.  A helium target leads to another important advantage, as the number of GPDs 
defined for a hadron depends on its spin. The structure of a spin zero nucleus, such as 
$^4$He, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case. This significantly
simplifies the interpretation of the data and allows a model independent
extraction of the $^4$He CFF ($\mathcal{H}_{A}$) presented at the
end of this letter.

@@

The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center of CLAS. For DVCS 
experiments, the CLAS baseline design \cite{Mecking:2003zu} is supplemented 
with an inner calorimeter (IC) and a solenoid. The IC extends the photon 
detection acceptance of CLAS to polar angles as low as 4$^{\circ}$. The 
low-energy M\o{}ller electrons produced in the target form a very high rate 
background that is suppressed by a 5 Tesla solenoid placed around the target.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. In Figure~\ref{fig:RTPC} a picture of 
RTPC installed in the experimental hall, and the rendering showing detector 
components and the $^4$He detection concept are presented. The $^4$He gaseous 
target, a $25$ cm long Kapton straw with $27~\mu$m thick wall, was part of the RTPC
assembly and installed on the axis of the detector. The RTPC was calibrated specifically for the detection 
of $^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one 
electron, one $^4$He, and at least one photon are detected in the final state.
Electrons are identified using measured momentum, time, and energy in the fiducial 
volume of the CLAS system's drift chambers, Cerenkov counters, scintillator counters, and 
electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in the RTPC using time, 
track quality, and energy loss cuts for tracks in the fiducial region. In 
addition, we apply a vertex matching cut to ensure that the electron and helium
nucleus originate from the same position. The photons are detected in either
the IC or the CLAS electromagnetic calorimeter. Note that even though the DVCS 
reaction has only one real photon in the final state, events with more than one 
good photon are not discarded at this stage. This is motivated by the fact 
that, while soft photons are likely to be produced in random coincidence, they 
cannot be mistaken for the large energy DVCS photons ($>2$ GeV).
The most energetic photon is always considered as the DVCS photon candidate.

@@

%asymmetries
In this work, the physics observable extracted using coherent DVCS events is
the Beam Spin Asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
measured as the difference of cross sections of the reaction at opposite beam 
helicities normalized to the total cross section:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
section for a positive (negative) beam helicity. 
In this ratio, luminosity normalization and
detector efficiencies largely cancel and $A_{LU}$ can be expressed in
terms of helicity-state yields ($N^{+/-}$)
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $P_{B}$ is the beam polarization.

%most of uncertainties of the 
%experimental normalization and in detector efficiencies will cancel out.

The DVCS reaction is experimentally indistinguishable from the well-known 
Bethe-Heitler (BH) process, where the final photon is emitted either from the 
incoming or the outgoing leptons. At leading twist and leading order, the 
deeply virtual photon production cross section is composed of BH, DVCS, and 
interference terms. While the BH is not sensitive to GPDs and does not carry 
information about the partonic structure of the hadronic target, its 
interference with the DVCS reaction is sensitive to GPDs enhancing the DVCS 
small cross section at the kinematical regions explored at Jefferson Lab. The 
amplitudes of the three terms can be approximated as a finite sum of Fourier 
harmonics, as shown for the nucleon in \cite{Belitsky:2001ns} and for the 
spin-zero targets in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these 
approximations, the beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can 
then be expressed as:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
depend on azimuthal angle $\phi$, the nuclear form factor 
$F_A(t)$, $Q^2$ and $x_B$. These factors are expressed as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi),\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} 
   \cos(2\phi),\\ \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
C_{++}(0) +  C_{++}(1) cos(\phi) \right),\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2},
\end{eqnarray}
\normalsize
where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
in the leptonic tensor.  The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

In this work the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
for a wide range of kinematics. We identified two main backgrounds to our 
measurement, accidental coincidences and exclusive coherent $\pi^0$ production.  
The accidentals have particles originating from different events, and we 
estimate their  contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with an electron and 
helium originating from different vertices. Regarding the $\pi^0$ production, 
it can easily be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the importance of this background, we developed an event generator 
calibrated on the experimental yield of exclusive $\pi^0$ measured by our 
experiment. We used this generator together with a GEANT3 simulation of our 
detector to estimate the ratio between the number of $\pi^0$ events where the 
two photons are detected and those that is misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data.  Depending on the kinematics, we found contaminations of 
2 to 4\%. The study of systematic uncertainties showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%). However, added quadratically,the total systematic 
uncertainty is about 10\%, which is significantly smaller than statistical 
uncertainties in all kinematical bins.

Due to limited statistics, dependence on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In Figure \ref{fig:alu}, $A_{LU}$ 
for the three sets of binning is presented. The curves on the plots are fits 
with the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and 
imaginary parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit. 
In Figure \ref{fig:alu90} the $Q^2$, $x_{B}$, and $-t$-dependencies of the 
fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and 
$-t$-dependencies are compared to theoretical calculations performed by 
S.~Liuti and K.~Taneja \cite{simonetta_2}. The model relies on the impulse 
approximation and uses advanced spectral functions of nuclei. The calculations 
are at slightly different kinematics than our data but still provide some 
guidance. The experimental results appear to have larger asymmetries than the 
calculations. These differences may arise from nuclear effects, such as 
long-rage interactions, which are not taken into account in the model.

@@

The $Q^2$, $X_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
Figure \ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
nucleons, each interacting independently with 
the probe. The Convolution-Dual model is based on nucleon GPDs from the dual 
parametrization \cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon 
GPDs  from the VGG model and is based on the double distributions ansatz 
\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on 
the impulse approximation and uses advanced spectral functions of  nuclei that 
account for all configurations of the final nuclear system and the binding 
effects between the nucleons.

The results in Figure \ref{fig:CFF_HA} show that the extraction of the CFF
from the beam spin asymmetry is possible without any model dependent 
assumptions. The amplitude and the dependencies observed as a function of 
$Q^{2}$, $x_B$, and $-t$ are in agreement 
with the theoretical expectations. One can see a difference between the 
precision of the extracted imaginary and real parts, which is expected from
Eq.~\ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. While the 
accuracy of our results does not allow to discriminate between the models, they 
demonstrate possibility of extraction of the CFF of spin 0 target in a model 
independent way.
